On Secure Delegation of SampBQP with a Classical Client

### 2019-11-23 hamiltonian.tex
Write intro for Hamiltonian section

Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper.

@@

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$.
\end{definition}

@@

\begin{definition}
	Let $C(x)$ be a quantum circuit. Then let $H_{C(x)}$ be with the following properties: TODO
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item 0 eigenvalue ground state and has certain form TODO type it out
		\item at least whatever eigenvalue in all other dimensions
		\item has ground state of a particular form we like
	\end{itemize}
\end{definition}

TODO Theorem statement for XZ LH and whatnot

\subsection{Preprocessing circuit}

>>>>

Here we lay our theoretical fundation by describing a reduction from $\SampBQP$ that we'll use throughout this paper. Here we'll only state the theorems, and prove them later in the subsections.

@@

\begin{definition}
	Let $\mathcal{G}_{XZ}=\set{U_0\otimes U_1\otimes\ldots\otimes U_n: U_i\in\set{I,X,Z}}$. TODO maybe force at most $k$ non-identity components here?
\end{definition}

Then we define a certain form of quantum circuit that is still universal.

\begin{definition}
	Let $C$ be an XZ-circuit if $C=U_T\ldots U_1$ where $U_i\in\spn\mathcal{G}_{XZ}$.
\end{definition}

\begin{theorem}
	Given a circuit $C$ and classical input $x$, a $BPP$ machine can reduce it to an XZ-circuit $C'$ and classical input $x'$.
\end{theorem}

@@

\begin{definition}
	Let $C(x)$ be an XZ-circuit. Then let $H_{C(x)}$ be with the following properties:
	\begin{itemize}
		\item $H_{C(x)}$ can be written as $\sum_{S\in\mathcal{G}_{XZ}} d_S S$, where each $S$ has at most constantly many non-identity components.
		\item It has an eigenvector $\ket{\psi_{C(x)}}=TODO$ with eigenvalue $0$.
		\item Let $\ket\phi$ be such that $\braket{\phi|\psi_{C(x)}}=0$, then $\braket{\phi|H_{C(x)}|\phi}>\frac{3}{4}$.
	\end{itemize}
\end{definition}

\begin{theorem}
	Given XZ-circuit $C$ and classical $x$, a $\BPP$ machine can construct a description of $H_{C(x)}$ in polynomial time.
\end{theorem}

\begin{theorem}
	Given XZ-circuit $C$ and $x$, there exists an quantum algorithm that accepts $\ket{\psi_{C(x)}}$ with probability... TODO that only uses $X$ and $Z$ measurements?
\end{theorem}

Lastly, before we present their proofs, we make an observation.

\begin{observation}
	Given XZ-circuit $C$ and $x$, one can first pad $C$ with identity matrices at the end, doubling its number of gates and obtain $C'$. One can then measure the last register of $\psi_{C'(x)}$ and obtain with probabiliy $\frac{1}{2}$ the state $C(x)$.
\end{observation}

\subsection{XZ-circuits}

Here we prove that XZ-circuits are universal. After this subsection, we'll be able to assume without loss of generality that all quantum circuits are XZ-circuits.
